### 2015-06-02 adp.tex
Cosmetics and some comments, especially on the proof of Lemma 8.4

\section{Approximate Dynamic Programming}
\emph{Curse-of-Dimensionality} is a term used to denote the fact that the number of states grows exponentially in the number of state variables. Most MDPs arising in practical applications suffer from the curse, i.e., have large number of states and it is difficult to compute $J^*/J_u\in \R^n$ exactly in such scenarios. Approximate dynamic programming (ADP) \cite{lspi,lspe,ALP,wang2014approximate} methods compute an approximate value function $\tilde{J}$ instead of $J^*/J_u$. In order to tackle the curse, ADP methods resort to dimensionality reduction by parameterizing the value function and/or the policy. Value-function based ADP methods form an important subclass of ADP methods whose brief overview is given below.
\subsection{Value-Function based ADP}
In the value-function based ADP schemes a parameterized family is chosen and the approximate value-function $\tilde{J}$ is picked from the chosen parameterized class.
Once the approximate value function $\tilde{J}$ is computed, a sub-optimal policy $\tilde{u}$ can be obtained as the one-step greedy policy with respect to $\tilde{J}$ by making use of \eqref{subpol}.
The following lemma characterizes the degree of sub-optimality of the greedy policy $\tilde{u}$.
\begin{lemma}\label{subopt}
Let $\tilde{J}$ be the approximate value function and $\tilde{u}$ be as in \eqref{subpol}, then 
\begin{align}
||J^*-J_{\tilde{u}}||_\infty \leq \frac{2}{1-\alpha}||J^*-\tilde{J}||_\infty.
\end{align}
\end{lemma}
The quality of any ADP method depends on the approximation guarantees it offers for the quantities $||J^*-\tilde{J}||$ and $||J^*-J_{\tu}||$, where $||\cdot||$ is an appropriate norm. The term  $||J^*-\tilde{J}||$ denotes the error in prediction and $||J^*-J_{\tu}||$ denotes the loss in performance resulting from the sub-optimal policy $\tu$ with respect to the optimal policy $u^*$. Of the two error terms, $||J^*-J_{\tu}||$ is more important because ultimately we are interested in coming up with a useful policy. In the context of ADP methods, the control and prediction problems are said to be addressed when the error terms $||J^*-\tilde{J}||$ and $||J^*-J_{\tu}||$ are bounded by ``small'' constants.\\
\subsection{Linear Function Approximation}
The most widely used parameterized class to approximate the value-function is the linear function approximator (LFA). Under LFA, the value-function is approximated as $\tilde{J}=\Phi r^*$, with $\Phi=[\phi_1|\ldots|\phi_k]$ being an $n\times k$ feature matrix and $r^*$ is the parameter to be learnt.\\
There are two important approaches to value function approximation. Both the approaches start out with a basic solution method and appropriately introduce function approximation in it. The two approaches are:
\begin{enumerate}
\item The Projected Bellman Equation (PBE) which combines the BE and the linear least squares projection operator to project high dimensional quantities onto the subspace of the LFA.
\item The approximate linear programming formulation which introduces the LFA in the linear programming formulation. 
\end{enumerate}
A host of ADP methods are based on the PBE and have been found to be useful in practice. The main application of the PBE is for approximate policy evaluation, i.e., to compute $\tilde{J}_u$, an approximation to the value function $J_u$ of policy $u$. Due to the mismatch in the norms, i.e, the linear least squares projection operator based on the $L_2$-norm and the $L_\infty$-norm of the Bellman operator $T$, one cannot use the PBE to obtain a direct approximation to $J^*$. Thus in order to solve the problem of control, $\tilde{J}_u$ is used to compute a one-step greedy policy. However, again due to the mismatch in the norms, i.e., $L_2$-norm of the linear least squares projection and the $L_\infty$ norm required for policy improvement (Lemma~\ref{subopt}), the one-step greedy policy need not necessarily be an improvement. This leads to a phenomenon called \emph{policy-chattering} \cite{dpchapter} where looping within of bad policies can occur. Further, such policy-chattering can be demonstrated in simple examples as well \cite{dpchapter}. Thus, though the approximate value function obtained by solving the PBE offers guarantees for prediction it does not offer any guarantees for the control problem, a significant shortcoming of the PBE based methods.\\
The ALP formulation \cite{ALP} on the other hand does not suffer from issues such as policy-chattering, for the simple reason that it computes $\tilde{J}$ which is an approximation to $J^*$ and a one-step greedy policy $\tilde{u}$ obtained using $\tilde{J}$. In short, since there is only one policy that the ALP outputs there is no question of policy-chattering. Further, the ALP offers performance guarantees for both the error terms $||J^*-\tilde{J}||$ and $||J^*-J_{\tilde{u}}||$. Though the ALP is a complete method addressing both the control and prediction problems, it nevertheless suffers from an important limitation in the form of large number of constraints (as large as the size of the state space). This limitation has been addressed in literature by sampling only a fewer tractable constraints to formulate a reduced linear program (RLP). The RLP has been shown to perform well in practice \cite{ALP,CS,CST}, but theoretical performance guarantees \cite{CS} are available for a specific RLP obtained under idealized assumptions. In this paper, by providing a sound theoretical analysis of the RLP, we aim to show that RLP is a complete method that addresses both the prediction and the control problems.
We achieve this by developing and presenting a comprehensive theoretical framework to understand the constraint reduction/approximation procedure.\\

>>>>

%!TEX root =  autocontgrlp.tex
\section{Approximate Dynamic Programming}
\emph{Curse-of-dimensionality} is a term used to denote the fact that the number of states grows exponentially in the number of state variables. \todoc{This itself won't be a curse, would it be? The problem is that the computation cost also grows exponentially. Note that we never defined what we mean by state variables.}
Most MDPs arising in practical applications suffer from the curse, i.e., have large number of states and it is difficult to compute $J^*/J_u\in \R^n$ exactly in such scenarios. Approximate dynamic programming (ADP) \cite{lspi,lspe,ALP,wang2014approximate} methods compute an approximate value function $\tilde{J}$ instead of $J^*/J_u$. In order to tackle the curse, ADP methods resort to dimensionality reduction by parameterizing the value function and/or the policy. Value-function based ADP methods form an important subclass of ADP methods whose brief overview is given below.

\subsection{Value-Function based ADP}
In the value-function based ADP schemes a parameterized family is chosen and the approximate value-function $\tilde{J}$ is picked from the chosen parameterized class.
Once the approximate value function $\tilde{J}$ is computed, a sub-optimal policy $\tilde{u}$ can be obtained as the one-step greedy policy with respect to $\tilde{J}$ by making use of \eqref{subpol}.
The following lemma characterizes the degree of sub-optimality of the greedy policy $\tilde{u}$.
\begin{lemma}\label{subopt}
Let $\tilde{J}$ be the approximate value function and $\tilde{u}$ be as in \eqref{subpol}, then 
\begin{align}
||J^*-J_{\tilde{u}}||_\infty \leq \frac{2}{1-\alpha}||J^*-\tilde{J}||_\infty\,.
\end{align}
\end{lemma}
The quality of any ADP method depends on the approximation guarantees it offers for the quantities $||J^*-\tilde{J}||$ and $||J^*-J_{\tu}||$, where $||\cdot||$ is an appropriate norm. The term  $||J^*-\tilde{J}||$ denotes the error in prediction and $||J^*-J_{\tu}||$ denotes the loss in performance resulting from the sub-optimal policy $\tu$ with respect to the optimal policy $u^*$. Of the two error terms, $||J^*-J_{\tu}||$ is more important because ultimately we are interested in coming up with a useful policy. In the context of ADP methods, the control and prediction problems are said to be addressed when the error terms $||J^*-\tilde{J}||$ and $||J^*-J_{\tu}||$ are bounded by ``small'' constants.

\subsection{Linear Function Approximation}
The most widely used parameterized class to approximate the value-function is the linear function approximator (LFA). Under LFA, the value-function is approximated as $\tilde{J}=\Phi r^*$, with $\Phi=[\phi_1|\ldots|\phi_k]$ being an $n\times k$ feature matrix and $r^*$ is the parameter to be learnt.

There are two important approaches to value function approximation. Both the approaches start out with a basic solution method and appropriately introduce function approximation in it. The two approaches are:
\begin{enumerate}
\item The Projected Bellman Equation (PBE) which combines the BE and the linear least squares projection operator to project high dimensional quantities onto the subspace of the LFA.
\item The approximate linear programming formulation which introduces the LFA in the linear programming formulation. 
\end{enumerate}
A host of ADP methods are based on the PBE and have been found to be useful in practice. The main application of the PBE is for approximate policy evaluation, i.e., to compute $\tilde{J}_u$, an approximation to the value function $J_u$ of policy $u$. Due to the mismatch in the norms, i.e, the linear least squares projection operator based on the $L_2$-norm and the $L_\infty$-norm of the Bellman operator $T$, one cannot use the PBE to obtain a direct approximation to $J^*$. Thus in order to solve the problem of control, $\tilde{J}_u$ is used to compute a one-step greedy policy. However, again due to the mismatch in the norms, i.e., $L_2$-norm of the linear least squares projection and the $L_\infty$ norm required for policy improvement (Lemma~\ref{subopt}), the one-step greedy policy need not necessarily be an improvement. This leads to a phenomenon called \emph{policy-chattering} \cite{dpchapter} where looping within of bad policies can occur. Further, such policy-chattering can be demonstrated in simple examples as well \cite{dpchapter}. Thus, though the approximate value function obtained by solving the PBE offers guarantees for prediction it does not offer any guarantees for the control problem, a significant shortcoming of the PBE based methods.

The ALP formulation \cite{ALP} on the other hand does not suffer from issues such as policy-chattering, for the simple reason that it computes $\tilde{J}$ which is an approximation to $J^*$ and a one-step greedy policy $\tilde{u}$ obtained using $\tilde{J}$. In short, since there is only one policy that the ALP outputs there is no question of policy-chattering. Further, the ALP offers performance guarantees for both the error terms $||J^*-\tilde{J}||$ and $||J^*-J_{\tilde{u}}||$. Though the ALP is a complete method addressing both the control and prediction problems, it nevertheless suffers from an important limitation in the form of large number of constraints (as large as the size of the state space). This limitation has been addressed in literature by sampling only a fewer tractable constraints to formulate a reduced linear program (RLP). The RLP has been shown to perform well in practice \cite{ALP,CS,CST}, but theoretical performance guarantees \cite{CS} are available for a specific RLP obtained under idealized assumptions. In this paper, by providing a sound theoretical analysis of the RLP, we aim to show that RLP is a complete method that addresses both the prediction and the control problems.
We achieve this by developing and presenting a comprehensive theoretical framework to understand the constraint reduction/approximation procedure.

### 2015-06-02 alubp.tex
Resolving conflict marks (<<<HEAD)
Cosmetics and some comments, especially on the proof of Lemma 8.4

r_c\stackrel{\Delta}{=}\min_{r\in \chi} &c^\top \Phi r,\nn\\
\text{s.t}\mb &W^\top E \Phi r\geq W^\top HJ, W \in \R^{nd\times m}_+ .

@@

The unique fixed point $\hv$ of the iteration in \eqref{apvi} and the solution $\hj$ of the GRLP obey $\hj\geq\hv$.

@@

Follows in a similar manner as the proof of Lemma~\ref{relation1}. To elaborate, let $\Phi r_1, \Phi r_2,\ldots,\Phi r_n$ be solutions to the GRLP in \eqref{grlp} for $c=e_1, e_2,\ldots,e_n$ respectively. Now consider the iterative scheme in \eqref{apvi} with $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$. It is clear from the definition of $V_0$ that $\hj(i)\geq\Phi r_i(i)\geq V_0(i)$, $i=1,\ldots,n$. Also from the monotone property of $T$ we have 
\Phi r_i&\geq V_0,\nn\\
H\Phi r_i&\geq H V_0,\mbox{we also have}\nn\\
E\Phi r_i\geq H\Phi r_i&\geq HV_0,\mb\text{by taking component-wise minimum},\nn\\
E V_0\geq H V_0.

@@

Let $\hv$, $\bj$ be as in Theorem~\ref{mt1} and let $r^*\stackrel{\Delta}{=}\arg\min_{r\in \R^k}||J^*-\Phi r||_\infty$, then

>>>>

r_c\stackrel{\Delta}{=} & \argmin_{r\in \chi} c^\top \Phi r,\nn\\
& \text{s.t.}\,\,\, W^\top E \Phi r\geq W^\top HJ,\,\, W \in \R^{nd\times m}_+ .

@@

The unique fixed point $\hv$ of the iteration in \eqref{apvi} and the solution $\hj$ of the GRLP \eqref{grlp} obey $\hj\geq\hv$.

@@

The proof follows in a similar manner as the proof of Lemma~\ref{relation1}. To elaborate, let $\Phi r_1, \Phi r_2,\ldots,\Phi r_n$ be solutions to the GRLP in \eqref{grlp} for $c=e_1, e_2,\ldots,e_n$ respectively. Fix some other $c\in [0,1]^n$, $\sum_i c(i)=1$.
Now consider the iterative scheme in \eqref{apvi} with $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$. 
It is clear from the definition of $V_0$ that $\hj(i),(\Phi r_j)(i)\geq(\Phi r_i)(i)$, $i=1,\ldots,n$.
In particular, it follows that $V_0(i) =( \Phi r_i)(i)$ and so
$\Phi r_i \geq V_0$.
From the monotone property of $T$ (viz. $H$) we have 
$H\Phi r_i\geq H V_0$ and also, by minimizing component-wise
$E\Phi r_i\geq H\Phi r_i\geq HV_0$. Thus,
$E V_0\geq H V_0$. 
\todoc[inline]{I lost why this was needed.
I think the proof would be much easier to understand if we introduced $r_{c,J} = \argmin_{r} \{ c^\top \Phi r \,|\, W^\top E \Phi r \ge W^\top H J\}$. We could start by saying we need $V_1\le V_0 \le \hj$ because then Lemma~\ref{tgmonotone} will give the desired result. Next, $V_0\le \hj$ holds because on the one hand, $\hj(i) \ge (\Phi r_i)(i)$ for any $i$, while on the other hand,
$(\Phi r_j)(i) \ge (\Phi r_i)(i)$ also holds for any $i,j$, hence $V_0(i)  = (\Phi r_i)(i)$. 
Now, for showing that $V_1 \le V_0$ holds, fix any $i$. We need to show that $(\hg V_0)(i) = \min_j (\Phi r_{e_j,V_0})(i) = (\Phi r_{e_i,V_0})(i)$ is less than $V_0(i)$. By the definition of $r_{e_j,V_0}$ we know that $(\Phi r_{e_i,V_0})(i) \le (\Phi r)(i)$
holds for any $r$ such that $W^\top E \Phi r \ge W^\top H V_0$. Thus, it suffices to show that $r_i$ satisfies this latter inequality,
i.e., $W^\top E \Phi r_i \ge W^\top H V_0$. For this, it clearly sufficient if $\Phi r_i \ge V_0$. This however directly follows 
from the definition of $V_0$.
}

@@

Let $\hv$, $\bj$ be as in Theorem~\ref{mt1} and let $r^*\stackrel{\Delta}{=}\argmin_{r\in \R^k}||J^*-\Phi r||_\infty$, then

### 2015-06-02 basic.tex
small edits, mostly typography + some comments
Cosmetics and some comments, especially on the proof of Lemma 8.4

\small
\begin{align}\label{mdplp}
\min_{J\in \R^n} &c^\top J\nn\\
\text{s.t}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'), \mb\forall s\in S, a \in A,
\end{align}
\normalsize
where $c\in \R^n_+$ is any vector whose components are all non-negative. One can show that $J^*$ is the solution to the LP formulation \eqref{mdplp} \cite{BertB}. 
Also, of the three methods, value iteration and LP formulation are value function based methods, i.e., they compute $J^*$ directly and then $u^*$ is obtained by plugging $J^*$ in \eqref{bellpol}.\\
While the basic methods (i.e., VI, PI and LP) can be used to compute exact values $J^*$ and $u^*$ for MDPs with a small number of states, they are computationally expensive in the case of MDPs with a large number of states.\\

>>>>

\begin{align}\label{mdplp}
\begin{split}
\min_{J\in \R^n} \,&c^\top J\\
\text{s.t}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'), \mb s\in S, a \in A,
\end{split}
\end{align}
where $c\in \R^n_+$ is any vector whose components are all non-negative. One can show that $J^*$ is the solution to the LP formulation \eqref{mdplp} \cite{BertB}. 
Also, of the three methods, value iteration and LP formulation are value function based methods, i.e., they compute $J^*$ directly and then $u^*$ is obtained by plugging $J^*$ in \eqref{bellpol}.

While the basic methods (i.e., VI, PI and LP) can be used to compute exact values $J^*$ and $u^*$ for MDPs with a small number of states, they are computationally expensive in the case of MDPs with a large number of states.

### 2015-06-02 grlp.tex
Cosmetics and some comments, especially on the proof of Lemma 8.4

\section{Generalized Reduced Linear Program}
In this section we present the generalized reduced linear program (GRLP) which is obtained by appropriately extending the definition of the RLP. An important property that should carry over from the RLP is that the feasible set of the GRLP should also be a superset of the feasible set of the ALP. A natural way to achieve this is to replace the set of sampled constraints in the RLP by a set of constraints which are obtained as linear combinations of the original constraints of the ALP. Formally, we define the generalized reduced linear program (GRLP) as below:
\begin{align}\label{grlp}
\min_{r\in \chi} &c^\top \Phi r,\nn\\
\text{s.t}\mb & W^\top E\Phi r\geq W^\top H \Phi r, 
\end{align}
where $W \in \R_+^{nd\times m}$ is an $nd\times m$ matrix with all nonnegative entries and $\chi \subset \R^k$ is any bounded set such that $\hj \in \chi$. Thus the $i^{th}$ ($1\leq i\leq m$) constraint of the GRLP is a positive linear combination of the original constraints of the ALP. Constraint reduction is achieved by choosing $m<<nd$. The key difference between the RLP in \eqref{rlpshort} and the GRLP in \eqref{grlp} despite their similar structure is that while $\M$ is a matrix of only zeros and ones, $W$ is a matrix of positive entries alone. Also note that an RLP is trivially a GRLP as well. Unless specified otherwise we use $\hr$ to denote the solution to the GRLP in \eqref{grlp}, $\hj=\Phi \hr$, to denote the corresponding approximate value function and $\hu$ to denote the greedy policy with respect to $\hj$.\par
Note that we want to avoid certain uninteresting and trivial cases of $W$ matrix such as $W=0$ or an entire column of $W$ being zero (which means no constraint is generated with respect to that column). Thus it is intuitive to demand that every column of $W$ should be non-negative and have at least one entry which is strictly positive. Also, normalizing columns of $W$ so that they sum to $1$ does not make any difference to the constraints of the RLP. Keeping these in mind we also assume the following throughout the rest of the paper:
\begin{assumption}\label{wassump}
$W \in \R^{nd\times m}_+$ is a full rank $nd\times m$  matrix (where $m<<nd$) and each of its column sums equals $1$.
\end{assumption}
The above assumption is just a technical condition that eliminates uninteresting choices such as $W=0$ or cases when certain columns of $W$ have all zeros, which implies that the corresponding column generates no constraint.
\input{cartoon}
The rest of the paper develops analytically various performance bounds and our main results provide the following:
\begin{enumerate}
\item A bound for $||J^*-\hj||$, the error between the approximate value function $\hj$ as computed by the GRLP and the optimal value function $J^*$;
\item a bound for $||J^*-J_{\hu}||$, the loss in performance due to the greedy policy $\hu$ measured with respect to the optimal policy; and
\item an important result on constraint sampling.
\end{enumerate}
We achieve the above via two novel $\max$-norm contraction operators namely the least upper bound (LUB) projection operator (denoted by $\Gamma$) and the approximate least upper bound (ALUB) projection operator (denoted by $\hat{\Gamma}$). We bound the error due to constraint approximation by analyzing the fixed points of the operators $\Gamma$ and $\hg$. We first establish our results in the $L_\infty$-norm and then extend the same in a modified $L_\infty$-norm. The schematic in Fig. ~\ref{schematic} provides a pictorial representation of what shall follow in the next three sections.
\FloatBarrier
\input{schematic}

>>>>

%!TEX root =  autocontgrlp.tex
\section{Generalized Reduced Linear Program}
In this section we present the generalized reduced linear program (GRLP) which is obtained by appropriately extending the definition of the RLP. An important property that should carry over from the RLP is that the feasible set of the GRLP should also be a superset of the feasible set of the ALP. A natural way to achieve this is to replace the set of sampled constraints in the RLP by a set of constraints which are obtained as linear combinations of the original constraints of the ALP. Formally, we define the generalized reduced linear program (GRLP) as below:
\begin{align}\label{grlp}
\begin{split}
\min_{r\in \chi}\, &c^\top \Phi r,\\
\text{s.t}\mb & W^\top E\Phi r\geq W^\top H \Phi r, 
\end{split}
\end{align}
where $W \in \R_+^{nd\times m}$ is an $nd\times m$ matrix with all nonnegative entries and $\chi \subset \R^k$ is any bounded set such that $\hj \in \chi$. \todoc{Is not $\hj\in \R^n$?
Moreover, later often $\chi$ is not taken into account. 
Also, the role of $\chi$ is never explained. Do we want to keep $\chi$ or maybe we should just remove it?
Further, $\hj$ is not really well defined. We need to defined $r_c$ and then set $\hj = \Phi r_c$.
}
Thus the $i^{th}$ ($1\leq i\leq m$) constraint of the GRLP is a positive linear combination of the original constraints of the ALP. Constraint reduction is achieved by choosing $m<<nd$. The key difference between the RLP in \eqref{rlpshort} and the GRLP in \eqref{grlp} despite their similar structure is that while $\M$ is a matrix of only zeros and ones, $W$ is a matrix of positive entries alone. Also note that an RLP is trivially a GRLP as well. Unless specified otherwise we use $\hr$ to denote the solution to the GRLP in \eqref{grlp}, $\hj=\Phi \hr$, to denote the corresponding approximate value function and $\hu$ to denote the greedy policy with respect to $\hj$.\par
Note that we want to avoid certain uninteresting and trivial cases of $W$ matrix such as $W=0$ or an entire column of $W$ being zero (which means no constraint is generated with respect to that column). Thus it is intuitive to demand that every column of $W$ should be non-negative and have at least one entry which is strictly positive. Also, normalizing columns of $W$ so that they sum to $1$ does not make any difference to the constraints of the RLP. Keeping these in mind we also assume the following throughout the rest of the paper:
\begin{assumption}\label{wassump}
$W \in \R^{nd\times m}_+$ is a full rank $nd\times m$  matrix (where $m<<nd$) and each of its column sums equals $1$.
\end{assumption}
The above assumption is just a technical condition that eliminates uninteresting choices such as $W=0$ or cases when certain columns of $W$ have all zeros, which implies that the corresponding column generates no constraint.
\input{cartoon}
The rest of the paper develops analytically various performance bounds and our main results provide the following:
\begin{enumerate}
\item A bound for $||J^*-\hj||$, the error between the approximate value function $\hj$ as computed by the GRLP and the optimal value function $J^*$;
\item a bound for $||J^*-J_{\hu}||$, the loss in performance due to the greedy policy $\hu$ measured with respect to the optimal policy; and
\item an important result on constraint sampling.
\end{enumerate}
We achieve the above via two novel $\max$-norm contraction operators namely the least upper bound (LUB) projection operator (denoted by $\Gamma$) and the approximate least upper bound (ALUB) projection operator (denoted by $\hat{\Gamma}$). We bound the error due to constraint approximation by analyzing the fixed points of the operators $\Gamma$ and $\hg$. We first establish our results in the $L_\infty$-norm and then extend the same in a modified $L_\infty$-norm. The schematic in Fig. ~\ref{schematic} provides a pictorial representation of what shall follow in the next three sections.
\FloatBarrier
\input{schematic}

### 2015-06-02 improv.tex
small edits, mostly typography + some comments
Cosmetics and some comments, especially on the proof of Lemma 8.4

\section{Improved Bounds}\label{sec:improv}
In this section, we present improved error bounds by making use of Lyapunov functions. 
\begin{lemma}\label{bestbndmn}
Let $r^*\in \R^k$ be defined as $r^*\stackrel{\Delta}{=}\arg\min_{r\in R^k}||J^*-\Phi r||_{\infty,1/\psi}$, then 
\begin{align}
||J^*-\bj||_{\infty,1/\psi}\leq 2||J^*-\Phi r^*||_{\infty,1/\psi}.
\end{align}
\end{lemma}
\begin{proof}
The result follows from the definition of $\Gamma$ in \eqref{gamdef}, Assumption~\ref{lyap} and the fact that $\Phi r^*+||J^*-\Phi r^*||_{\infty,1/\psi} \psi\geq TJ^*$.
\end{proof}

@@

Let $\hv$, $\bj$ be as in Theorem~\ref{mt1} and let $r^*\stackrel{\Delta}{=}\arg\min_{r\in \R^k}||J^*-\Phi r||_{\infty,1/\psi}$ then

@@

We now recall Lemma~$4.3$ of \cite{ALP}.

@@

\Phi r'=\Phi r+||J^*-\Phi r||_{\mn}(\frac{1+\beta_{\psi}}{1-\beta_{\psi}})\psi.

>>>>

%!TEX root =  autocontgrlp.tex
\section{Improved Bounds}\label{sec:improv}
In this section, we present improved error bounds by making use of Lyapunov functions. 
\begin{lemma}\label{bestbndmn}
Let $r^*\in \R^k$ be defined as $r^*\stackrel{\Delta}{=}\argmin_{r\in R^k}||J^*-\Phi r||_{\infty,1/\psi}$, then 
\begin{align}
||J^*-\bj||_{\infty,1/\psi}\leq 2||J^*-\Phi r^*||_{\infty,1/\psi}.
\end{align}
\end{lemma}
\begin{proof}
The result follows from the definition of $\Gamma$ in \eqref{gamdef}, Assumption~\ref{lyap} and the fact that $\Phi r^*+||J^*-\Phi r^*||_{\infty,1/\psi} \psi\geq TJ^*$.
\end{proof}

@@

Let $\hv$, $\bj$ be as in Theorem~\ref{mt1} and let $r^*\stackrel{\Delta}{=}\argmin_{r\in \R^k}||J^*-\Phi r||_{\infty,1/\psi}$ then

@@

We now recall Lemma~$4.5$ of \cite{ALP}. \todoc{You had 4.3 here, but in the official journal version this seems to be Lemma 5 in Section 4.}

@@

\Phi r'=\Phi r+||J^*-\Phi r||_{\mn} \left(\frac{1+\beta_{\psi}}{1-\beta_{\psi}}\right)\, \psi.
